Timely Object Detection

### 2012-02-20 writeups/eccv12/eccv12.tex

@@

\todo{
Consider revising the above to make a single action compute all the scene classifiers at once.
}

Each classifier $L$ or feature computation $F$ has an expected cost of execution.
Depending on the setting, the cost can be defined in terms of algorithmic runtime analysis (e.g. $O(N^3)$), an idealized property such as number of \emph{flops}, or simply the empirical runtime on specific hardware.
We take the empirical approach: every executed action advances $t$, the \emph{time into episode}, by its empirical runtime.

@@

We define the \emph{belief state} $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$ (writing $P(C_i)$ to mean $P(C_i=1)$), the time into episode $t$, and other variables that will be discussed in \autoref{sec:value}.
The terminology of ``belief'' comes from reinforcement learning and refers to the distribution $P(\mathbf{C})$.

An action $a$ can result in a set of observations $o$ that can be used to update the belief state.
At the very least, the state records the fact that $a$ has been taken.
A classification \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b_0$ and action $a_0$ to the next pair $(b_1,a_1)$, and so on until $t$ exceeds $T_d$.
At that point, the policy is terminated and a new episode begins on a new image.

@@

\begin{table}
\centering
\caption{Summary of the notation used.}
\label{tab:notation}
\begin{tabular}{|l|l|}
	\hline
	$C_i$         & presence of at least one object of class $i$  \\ 
	$K$           & number of object classes                      \\ 
	$t$           & time into episode                             \\ 
	$T_s$, $T_d$  & start and deadline times                      \\ 
	$\mathcal{A}$ & set of actions                                \\ 
	$b_j$        	& belief state at step $j$                                 \\ 
	$\pi$         & policy, $\phi(b_s) \mapsto a \in \mathcal{A}$ \\ 
	\hline
\end{tabular}\end{table}

\subsection{Reward} \label{sec:reward}
The goal of our policy is Anytime performance, so it would be limiting to evaluate only at deadline time.
Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).
Toward this goal, we formulate a \emph{reward function} that encourages this behavior by assigning a score to a belief state.

Let's say that given deadline $T_d$ and some image, the policy had time to take $J$ actions.
The total expected reward of a policy $\pi$ is then defined as the sum of rewards
\begin{equation}
\mathbb{E}_\pi[\sum_{j=0}^J R(b_j)]
\end{equation}

@@

\subsubsection{Information gain}
A common approach to our kind of problem is to minimize uncertainty as quickly as possible.
Therefore we define the reward as a function of the negative residual entropy, following \cite{Gao2011}.

\todo{What's the difference here between minimizing entropy and maximizing expected information gain over the length of the episode?}

\subsection{The value function} \label{sec:value}
At each step, we want to pick the action that maximizes the expected rewards until the end of the episode.
We therefore define our policy as
\begin{equation}
\pi(b) = \argmax_{a \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a)
\end{equation}

@@

\section{Evaluation} \label{sec:evaluation}

>>>>

\begin{table}
\centering
\caption{Summary of the notation used.}
\label{tab:notation}
\begin{tabular}{|l|l|}
	\hline
	$C_i$         & presence of class $i$ \\ 
	$K$           & number of object classes \\ 
	$t$           & time into episode \\ 
	$T_s$, $T_d$  & start and deadline times \\ 
	$\mathcal{A}$ & set of actions \\ 
	$b_j$        	& belief state at step $j$ \\ 
	$\pi$         & policy, $\pi(b) \mapsto a \in \mathcal{A}$ \\ 
	\hline
\end{tabular}\end{table}

@@

\todo{
Revise the above to make a single action compute all the scene classifiers at once.
}

Each classifier $L$ or feature computation $F$ has an expected cost $c(\cdot)$ of execution.
Depending on the setting, the cost can be defined in terms of algorithmic runtime analysis, an idealized property such as number of \emph{flops}, or simply the empirical runtime on specific hardware.
We take the empirical approach: every executed action advances $t$, the \emph{time into episode}, by its empirical runtime.

@@

We define the \emph{belief state} $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$ (writing $P(C_i)$ to mean $P(C_i=1)$), the time into episode $t$, the set of executed actions $\mathcal{O}$, and other variables that will be discussed in \autoref{sec:value}.
\comment{The terminology of ``belief'' comes from reinforcement learning and refers to the distribution $P(\mathbf{C})$.}

An action $a$ can result in a set of observations $o$ that are used to update the belief state.
At the very least, the state records the fact that $a$ has been taken by adding it to the initially empty set $\mathcal{O}$.

A classification \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b_0$ and action $a_0$ to the next pair $(b_1,a_1)$, and so on until $t$ exceeds $T_d$.
At that point, the policy is terminated and a new episode begins on a new image.

@@

\subsection{The value function} \label{sec:value}
Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).
As our goal is to pick actions, we want to formulate a function that assigns a value to a potential action, given the current state of the decision process.
We will then be able to define our policy as simply
\begin{equation}
\pi(b) = \argmax_{a \in \mathcal{A} \setminus \mathcal{O}} V(b,a)
\end{equation}

We consider two formulations of the value function: one based on information gain, and one on the classification loss.

\subsubsection{Information gain}
negative residual entropy, following \cite{Gao2011}.

\todo{Write this out, and mention the greedy submodularity argument, to be made in a later section.}

\subsubsection{Classification loss}
\todo {Write this out. What to do with the cost here?}

\subsection{Reward} \label{sec:reward}
Let's say that given deadline $T_d$ and some image, the policy had time to take $J$ actions.
The total expected reward of a policy $\pi$ is then defined as the sum of rewards
\begin{equation}
\mathbb{E}_\pi[\sum_{j=0}^J R(b_j)]
\end{equation}

@@

At each step, we want to pick the action that maximizes the expected rewards until the end of the episode.
We therefore define our policy as
\begin{equation}
\pi(b) = \argmax_{a \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a)
\end{equation}

@@

\section{Evaluation} \label{sec:evaluation}
- show that the greedy policy works better than random and better than fixed-order
- show that the reinfrocement learning policy works better than greedy, at least for the non-infogain rewards.

\subsection{Classification}

\subsection{Detection}
We also evaluate using the task of detection (see \autoref{sec:problem}).
